The LBRY Trending Algorithm

### 2021-11-18 tex/ms.tex
Big numbers

>>>>

In the actual code, we store squashed trending values, i.e., $S(Z)$ in the
notation of this paper, for every claim. When claims are touched, the
squashed trending values are updated. At block height 1,000,000, which occurred
in 2021, unsquashed trending values would have been of order
\begin{align}
\exp\left(\frac{10^{6}}{576}\right) &\approx 10^{753}.
\end{align}
However, the squashed values are only of order $10^6 / 576 \approx 1736$.
Differences in squashed trending values, which determine the ordering of claims
in applications, occur in the third, fourth, and subsequent digits.
With double precision storage, the situation will remain acceptable for
centuries. For example, at block height 100 million, expected around 2496 AD,
squashed trending scores will be around 150,000, with plenty of remaining
significant digits to allow for sorting.
